Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-21 manuscript.Rmd
Added Asian social work journal.

@@

final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
    theme_bw()

>>>>

bigList <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n())
bigList$shortTitle <- abbreviate(bigList$title)

ggplot(bigList, aes(year, N, group = 1)) + geom_line(colour="#5e3c99") + 
    facet_wrap(~ title, ncol=7) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
    ylim(0, 150)

@@

final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
#    theme_bw() 
final.list.index$scaleScore <- scale(final.list.index$n)
final.list.index$hScaled <- scale(final.list.index$h5Index)
final.list.index <- arrange(final.list.index, scaleScore)

ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
    xlim(c(-3, 3))
